\documentclass[12pt]{article}

% Set landscape mode and custom margins for page while including space for the footer
\usepackage[includefoot, margin={0.5cm, 0.5cm}, landscape]{geometry}

% Used to reduce the spacing around section headers and titles.
% Format title headers by adjusting font size
% Set the spacing on all sides of the title to 0
\usepackage[compact]{titlesec}
\titleformat{\section}{\normalfont\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{*0}{0pt}

% Reduce spacing around list items
\usepackage{enumitem}
\setlist{nolistsep}

% Set line spacing
\usepackage{setspace}
\singlespacing

% Create a multicolumn layout
% Set the amount of separation between columns
% Draw a vertical rule between the columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{0.1pt}

% Add a frame around the content
\usepackage{mdframed}

% Custom footer (and header if I wanted)
\usepackage{fancyhdr}
\pagestyle{fancy}

% Set custom headers and footers for fancyhdr
\fancyhead{}
\fancyfoot[C]{Thunderstone Advance Summary Sheet v1.0}
\renewcommand{\headrulewidth}{0pt} 	% Remove horizontal rule from header
\renewcommand{\footrulewidth}{0pt}  % Remove horizontal rule from footer

% Custom frame style for mdframed
% The negative margin is needed to fix a weird spacing that I couldn't figure out
\mdfdefinestyle{customFrame}{%
    outerlinewidth = 0.4pt,
    innertopmargin = -0.3cm}

% Reduce whitespace in the enumerate list environment
\newenvironment{enumerateCustom}
{\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{enumerate}}

% Reduce whitespace in the itemize list environment
\newenvironment{itemizeCustom}
{\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{itemize}}

\begin{document}
\begin{mdframed}[style = customFrame]
\begin{multicols*}{2}

\section*{Setup}
\begin{enumerateCustom}
	\item Generate or pick scenario (see below). 
	\item Set out board and selected cards.
	\item Give each player starting deck of 6 Regular, 2 Longspear, 2 Torch, and 2 Thunderstone Shard cards.
\end{enumerateCustom}

\section*{Village Randomization - Monsters}
\begin{itemizeCustom}
	\item Shuffle monster randomizers. Reveal cards until 1 group of levels 1 through 3 are found. Remove matching card sets.
	\item Draw random Thunderstone Bearer card.
	\item Shuffle all monster cards together.
	\item Remove 10 cards and mix Thunderstone Bearer in. Place these cards under the shuffled monsters. This forms the Dungeon Deck.
	\item Fill empty ranks on dungeon board with monsters face up. This forms the Dungeon Hall.
\end{itemizeCustom}

\section*{Village Randomization - Village}
\begin{itemizeCustom}
	\item Pull $player count * 3$ each of the basic cards (Regular, Longspear, and Torch). Set out on board.
	\item Shuffle hero randomizers and reveal 4. Remove card sets. Arrange hero cards in level order starting with 1.
	\item Shuffle village randomizers. Reveal card and set out cards on board if spot is available. If no room on board for card type, skip it. Continue until 8 stacks have been set out. (Board won't be full)
\end{itemizeCustom}

\section*{Goal of the Game}
\section*{Player Turn}
\section*{End Game}

\end{multicols*}
\end{mdframed}
\end{document}
