\documentclass[12pt]{article}

% Set landscape mode and custom margins for page while including space for the footer
\usepackage[includefoot, margin={0.5cm, 0.5cm}, landscape]{geometry}

% Used to reduce the spacing around section headers and titles.
% Format title headers by adjusting font size
% Set the spacing on all sides of the title to 0
\usepackage[compact]{titlesec}
\titleformat{\section}{\normalfont\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{*0}{0pt}

% Reduce spacing around list items
\usepackage{enumitem}
\setlist{nolistsep}

% Set line spacing
\usepackage{setspace}
\singlespacing

% Create a multicolumn layout
% Set the amount of separation between columns
% Draw a vertical rule between the columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{0.1pt}

% Add a frame around the content
\usepackage{mdframed}

% Custom footer (and header if I wanted)
\usepackage{fancyhdr}
\pagestyle{fancy}

% Set custom headers and footers for fancyhdr
\fancyhead{}
\fancyfoot[C]{Dungeon Petz Summary Sheet v1.0}
\renewcommand{\headrulewidth}{0pt} 	% Remove horizontal rule from header
\renewcommand{\footrulewidth}{0pt}  % Remove horizontal rule from footer

% Custom frame style for mdframed
% The negative margin is needed to fix a weird spacing that I couldn't figure out
\mdfdefinestyle{customFrame}{%
    outerlinewidth = 0.4pt,
    innertopmargin = -0.3cm}

% Reduce whitespace in the enumerate list environment
\newenvironment{enumerateCustom}
{\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{enumerate}}

% Reduce whitespace in the itemize list environment
\newenvironment{itemizeCustom}
{\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{itemize}}

\begin{document}
\begin{mdframed}[style = customFrame]
\begin{multicols*}{2}

\section*{Setup}
\subsection*{General}
\begin{enumerateCustom}
	\item Set out Central Board. \textbf{2/3:} Use the side with arrows between spaces.
	\item Set out Progress Board. \textbf{2/3:} Use the side with 2/3 Imps in the corner.
	\item Give each player Burrow Board, Pet Display Board, Imps and Minion figures, and point tile.
	\item Pick a first player.
\end{enumerateCustom}

\subsection*{Progress Board}
\begin{enumerateCustom}
	\item Set purple progress marker on the "1" space.
	\item Each player places one of their Imps in the Imp spaces.
	\item Shuffle the blue and white Exhibition tiles and deal one to each space face down. Turn up the first one.
	\item Randomize the Customer tiles and deal one to each space face down. Turn up the first one.
\end{enumerateCustom}

\subsection*{Central Board}
\begin{enumerateCustom}
	\item \textbf{3:} Place one non-player Imp on the 3 action spaces marked with a dot. \textbf{2:} Block the 3 action spaces marked with a dot and the one 3 spaces away (following the arrows).
	\item Mix up the pets and place them face down. Draw 3 pets, set them to level 2 (2 bars showing) and place them in the lower half of the pet corral. \textbf{2/3:} Only draw 2 pets since a neutral Imp is blocking one of the action spaces.
	\item Draw one pet, set it to level 3, and place it in the upper half of the pet corral.
	\item Mix up the round artifact tiles and place them face down. Draw 2 and place them face up on the blue tents. \textbf{2:} Place no artifacts here for round one since a neutral Imp is blocking the action space.
	\item Sort the green and red food tokens and place them in the storage areas. Check the progress board to see how much food to put in each market stall for each round.
	\item Sort the Need Cards by color and shuffle.
	\item Set the Potion Card face down on the hospital building.
	\item Set out Suffering Tokens (gray), Manure Tokens (brown), and Mutation Tokens (purple/pink).
	\item Set one minion on score track and one on the exhibition tent.
	\item Set out the Gold Tokens in the bank on the board.
	\item Shuffle the rectangular Cage Addons. Draw 2 and place them face up on the board.
	\item Shuffle the Cages. Place 3 on the Cage spaces face up. \textbf{2:} Only place 2 since a neutral Imp is blocking an action space.
\end{enumerateCustom}

\subsection*{Player Board}
\begin{enumerateCustom}
	\item Give each player 2 Gold.
	\item Place 1 Manure Token in your starting Cage printed on your board.
	\item Draw 4 Need Cards, one of each color.
\end{enumerateCustom}

\section*{Goal of the Game}
You and your Imp family must raise the best pets around. The better pets you raise, the more the dungeon lords will like you, and the better your reputation. Be the family with most reputation to win the game.
\section*{Player Turn}
\section*{End Game}

\end{multicols*}
\end{mdframed}
\end{document}
