\documentclass[12pt]{article}

% Set landscape mode and custom margins for page while including space for the footer
\usepackage[includefoot, margin={0.5cm, 0.5cm}, landscape]{geometry}

% Used to reduce the spacing around section headers and titles.
% Format title headers by adjusting font size
% Set the spacing on all sides of the title to 0
\usepackage[compact]{titlesec}
\titleformat{\section}{\normalfont\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{*0}{0pt}

% Reduce spacing around list items
\usepackage{enumitem}
\setlist{nolistsep}

% Set line spacing
\usepackage{setspace}
\singlespacing

% Create a multicolumn layout
% Set the amount of separation between columns
% Draw a vertical rule between the columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{0.1pt}

% Add a frame around the content
\usepackage{mdframed}

% Custom footer (and header if I wanted)
\usepackage{fancyhdr}
\pagestyle{fancy}

% Set custom headers and footers for fancyhdr
\fancyhead{}
\fancyfoot[C]{Ginkgopolis Summary Sheet v1.0}
\renewcommand{\headrulewidth}{0pt} 	% Remove horizontal rule from header
\renewcommand{\footrulewidth}{0pt}  % Remove horizontal rule from footer

% Custom frame style for mdframed
% The negative margin is needed to fix a weird spacing that I couldn't figure out
\mdfdefinestyle{customFrame}{%
    outerlinewidth = 0.4pt,
    innertopmargin = -0.3cm}

% Reduce whitespace in the enumerate list environment
\newenvironment{enumerateCustom}
{\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{enumerate}}

% Reduce whitespace in the itemize list environment
\newenvironment{itemizeCustom}
{\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{itemize}}

\begin{document}
\begin{mdframed}[style = customFrame]
\begin{multicols*}{2}

\section*{Setup}
\begin{enumerateCustom}
	\item Place the 9 \emph{Building} tiles numbered 1, 2, and 3 in a 3x3 square.
	\item Place the 12 \emph{Urbanization} tokens in alphabetical order around the board.
	\item Shuffle the remaining \emph{Building} tiles and place in face down piles. For 2 or 3 player game, remove 6 random tiles without peeking!
	\item Form a deck by shuffling the 12 \emph{Urbanization} cards (A to L) and the 9 \emph{Building} cards that correspond to the starting building tiles. In 2 or 3 player game, discard the first 7 cards face up next to the deck.
	\item Sort the \emph{Building} cards numbered 4-20 by color and ascending order.
	\item Each player picks a color and places the resources in the general supply. Take 25/20/18/16 resources for a 2/3/4/5 player game.
	\item Each player gets a screen in their color and 2 \emph{New Hand} tokens.
	\item Give each player 4 character cards. Players take 1 card from their hand and pass the remainder left. Continue until everyone has 3. Then everyone reveals their character cards. In introductory game, each player receives a random set of 3 cards that are identified by the same number.
	\item Place character cards in front of player screen. Take the resources indicated by the starting character cards in the top-left corner. All items go behind your screen.
	\item Deal 4 cards from the deck to each player.
\end{enumerateCustom}

\section*{Goal of the Game}
Players are trying to accrue the most ``success'' points by the end of the game by operating and constructing buildings in the city of Ginkgopolis.

\section*{Playing the Game}
The game is divided into 3 phases:
\begin{enumerateCustom}
	\item Choose a card
	\item Resolve actions
	\item Prepare for the next round
\end{enumerateCustom}

\section*{Choose a Card}
Players simultaneously look at their hand of 4 cards, pick one, and place it face down in front of their screen. The card can be played by itself or with a \emph{Building} tile, depending on the action that you wish to perform. If playing it with a tile, select the tile behind your screen and place it face down on the card. Players may also discard a \emph{New Hand} token to discard all 4 cards and draw 4 new cards.

\section*{End Game}

\end{multicols*}
\end{mdframed}
\end{document}
