\documentclass[12pt]{article}

% Set landscape mode and custom margins for page while including space for the footer
\usepackage[includefoot, margin={0.5cm, 0.5cm}, landscape]{geometry}

% Used to reduce the spacing around section headers and titles.
% Format title headers by adjusting font size
% Set the spacing on all sides of the title to 0
\usepackage[compact]{titlesec}
\titleformat{\section}{\normalfont\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{*0}{0pt}

% Reduce spacing around list items
\usepackage{enumitem}
\setlist{nolistsep}

% Set line spacing
\usepackage{setspace}
\singlespacing

% Create a multicolumn layout
% Set the amount of separation between columns
% Draw a vertical rule between the columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{0.1pt}

% Add a frame around the content
\usepackage{mdframed}

% Custom footer (and header if I wanted)
\usepackage{fancyhdr}
\pagestyle{fancy}

% Set custom headers and footers for fancyhdr
\fancyhead{}
\fancyfoot[C]{Le Havre Summary Sheet v1.0}
\renewcommand{\headrulewidth}{0pt} 	% Remove horizontal rule from header
\renewcommand{\footrulewidth}{0pt}  % Remove horizontal rule from footer

% Custom frame style for mdframed
% The negative margin is needed to fix a weird spacing that I couldn't figure out
\mdfdefinestyle{customFrame}{%
    outerlinewidth = 0.4pt,
    innertopmargin = -0.3cm}

% Reduce whitespace in the enumerate list environment
\newenvironment{enumerateCustom}
{\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{enumerate}}

% Reduce whitespace in the itemize list environment
\newenvironment{itemizeCustom}
{\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{itemize}}

\begin{document}
\begin{mdframed}[style = customFrame]
\begin{multicols*}{2}

\section*{Setup}
\begin{enumerateCustom}
	\item Set out the 3 game boards (Use numbers in top left corner for ordering).
	\item Give each player 1 Person disc, 1 Ship marker, and 1 Game turn overview card.
	\item Shuffle the 7 supply disks and place them face-down in the water spaces. Place players' ships beside the first supply tile.
	\item Place out the goods and food supply tokens.
	\item Place the starting goods (Check text on offer spaces for amount).
	\item Give each player 5 Francs and 1 coal.
	\item Set 6 Special Building cards face-down onto the marked space.
	\item Set out the starting building cards (Construction Firm and 2 Building Firms).
	\item Set out the Standard Buildings. Only use a card that has a dark tick (Or light if playing the short version) for the current number of players. Divide the cards into 3 piles and sort them into descending order according to the Sort Number (top right).
	\item Sort the Round cards for the appropriate number of players according to the dark circled number (or light if playing the short version).
	\item Set out the Loan Cards, Round Overview card, and Food Production tokens.
\end{enumerateCustom}

\section*{Goal of the Game}
\section*{Player Turn}
\section*{End Game}

\end{multicols*}
\end{mdframed}
\end{document}
