\documentclass[12pt]{article}

% Set landscape mode and custom margins for page while including space for the footer
\usepackage[includefoot, margin={0.5cm, 0.5cm}, landscape]{geometry}

% Used to reduce the spacing around section headers and titles.
% Format title headers by adjusting font size
% Set the spacing on all sides of the title to 0
\usepackage[compact]{titlesec}
\titleformat{\section}{\normalfont\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{*0}{0pt}

\titleformat{\subsection}{\normalfont\bfseries}{\thesection}{0.6em}{}
\titlespacing*{\subsection}{0pt}{*0}{0pt}

\titleformat{\subsubsection}{\normalfont\bfseries\em}{\thesection}{0.3em}{}
\titlespacing*{\subsubsection}{0pt}{*0}{0pt}

% Reduce spacing around list items
\usepackage{enumitem}
\setlist{nolistsep}

% Set line spacing
\usepackage{setspace}
\singlespacing

% Create a multicolumn layout
% Set the amount of separation between columns
% Draw a vertical rule between the columns
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{0.1pt}

% Add a frame around the content
\usepackage{mdframed}

% Custom footer (and header if I wanted)
\usepackage{fancyhdr}
\pagestyle{fancy}

% Set custom headers and footers for fancyhdr
\fancyhead{}
\fancyfoot[C]{Castles of Burgundy Summary Sheet v1.0}
\renewcommand{\headrulewidth}{0pt} 	% Remove horizontal rule from header
\renewcommand{\footrulewidth}{0pt}  % Remove horizontal rule from footer

% Custom frame style for mdframed
% The negative margin is needed to fix a weird spacing that I couldn't figure out
\mdfdefinestyle{customFrame}{%
    outerlinewidth = 0.4pt,
    innertopmargin = -0.3cm}

% Reduce whitespace in the enumerate list environment
\newenvironment{enumerateCustom}
{\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{enumerate}}

% Reduce whitespace in the itemize list environment
\newenvironment{itemizeCustom}
{\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{itemize}}

\begin{document}
\begin{multicols*}{2}

\section*{Setup}
\begin{enumerateCustom}
	\item Place Silverlings, worker tiles, and white die by the board.
	\item Sort the 6-sided tiles by back color and place face-down by board.
	\item Shuffle the 42 goods tiles. Separate them into 5 face-down piles of 5 tiles. Place on spaces labeled A through E on the board. Set aside unused tiles.
	\item Place the 12 colored square bonus tiles on the board.
	\item Give each player
		\begin{itemizeCustom}
			\item 1 Player board with the Number 1 side face up.
			\item 1 castle (dark green 6-sided tile) place on middle space.
			\item 3 random good tiles from unused tiles placed face-up on upper left corner of player board. Same type goods stack.
			\item 2 dice and score tracker placed on victory point track.
			\item 1 Silverling.
		\end{itemizeCustom}
	\item Highest number roll determines start player. First player takes 1 worker, next 2 workers, and so on. 
	\item Place second playing piece to mark turn order on the track. First player is top of tower and last is the bottom.
	\item Give first player the white die.
\end{enumerateCustom}
\section*{Goal of the Game}
\section*{Gameplay}
The game plays out over 5 phases (A through E) each containing 5 rounds. Game flow:

\subsection*{Setup for each Phase}
\begin{itemizeCustom}
	\item Remove all 6-sided tiles from board. Leave ship, mine, and castles as they are all the same.
	\item Draw new 6-sided tiles and place them on the appropriately colored spaces. Only fill spaces marked with the number $\le$ number of players.
	\item Place 5 good tiles for this phase on the 5 round squares.
\end{itemizeCustom}

\subsection*{Setup for each Round}
\begin{itemizeCustom}
	\item All players roll their 2 dice.
	\item Roll the white die and place the current rounds good according to the result.
	\item All players now take their turn starting with the first player.
\end{itemizeCustom}

\section*{Player's Turn}
Carry out two actions, once per die. Worker tiles may be used to change the result of the dice. 1-6 or 6-1 wrapping is valid. Once per turn, you may purchase one tile from the black depot for 2 Silverlings.

\subsection*{Actions}
\subsubsection*{Take 6-sided tile}
Die value indicates from which depot the tile is taken. Place into storage on bottom-left of player board. Discard a tile if no space is available.

\subsubsection*{Add 6-sided tile to estate from storage}
Die value indicates which empty space to place the tile. Tile must be placed adjacent to previously placed tile(s) and match the space's color. Then:

\begin{itemizeCustom}
	\item "Ship" (blue) - Add to your storage all goods from any one depot. Only three colors of goods may be stored. Leave behind any goods that you can't store. Move turn-order piece right on thet rack one space. If occupied, stack on top of the other pieces. If new first player, take the white die.
	\item Knowledge (yellow) - Check the book.
	\item Animal (light green) - Get victory points based on how many animals are on the tile. If expanding a pasture, pre-existing animals of the same type are scored also. Note, same pasture doesn't necessitate immediate adjacency within the same pasture. (Ex. pg. 6)
	\item Castle (dark green) - Immediately take another action as if he had an extra die with any result.
	\item Mine (grey) - At the end of each pahse, receive 1 Silverling for this mine.
	\item Building (beige) - Immediately make a single use of that building's advantage (Ex. pg. 7). Note, no identical buildings in a city (connected beige region) are allowed.
\end{itemizeCustom}

\subsubsection*{Sell goods}
Die value indicates which type of goods can be sold. Place all sold goods face down in the sold goods square. Receive 1 Silverling and number of tiles * number of players VP. Note, all the goods of the type must be sold. None can be kept in reserve.

\subsubsection*{Take worker tiles}
Use any die result to take 2 worker tiles.

\section*{End of Phase}
Players receive 1 Silverling for each mine in their estate. Resolve any yellow "Knowledge" tiles have an end of phase effect.

\section*{End Game}

\end{multicols*}
\end{document}
